\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-13 jss/article.tex
hospital done

The estimated 95\% intervals are displayed on the right-side plot. We can clearly see that all the posterior mean (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line). But the most important information from this plot would be the range of each hospital's true death rate. Overall, as the sample size increases (size of dots) and as the posterior mean gets close to 0, the length of interval gets shorter, which the formula of posterior variance (6) implies. Although the fist interval does not include the observed sample mean, it can happen by chance considering these are 95\% intervals. Then, how reliable are these intervals? The method check will answer it.
\begin{CodeChunk}
\begin{CodeInput}
R> coverage(p, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 6cm]{hospital3.png}
\end{center}
\end{figure}
We generated 10,000 pseudo-datasets and estimated coverage probabilities in two ways, unbiased estimates (blue dashed line) and Rao-Blackwellized estimates. 
\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{school1.png}
\caption{Shrinkage and interval plots of 8 schools}
\end{center}
\end{figure}

>>>>

The estimated 95\% intervals are displayed on the right-side plot. We can clearly see that all the posterior mean (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line). But the most important information from this plot would be the range of each hospital's true death rate. Overall, as the sample size increases (size of dots) and as the posterior mean gets close to 0, the length of interval gets shorter, which the formula of posterior variance (6) implies. Although the fist interval does not include the observed sample mean, it can happen by chance considering these are 95\% intervals. Then, how reliable are these intervals? The method check will answer it.
\begin{CodeChunk}
\begin{CodeInput}
R> coverage(p, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 6cm]{hospital3.png}
\end{center}
\end{figure}
We generated 10,000 pseudo-datasets and estimated coverage probabilities by unbiased estimates (a blue dashed line) and Rao-Blackwellized estimates (a red line). Both lines are indistingishable from the horizontal line at 0.95 and the overall average coverage rate is 0.951 based on both estimation methods. Finally, this method check showed that the interval estimates from our hierarchical modeling (with Bayesian framework) on this dataset had a very good repeated sampling property.

\subsection[Unknown Second-level Mean and No Covariate]{8 Schools: Unknown Second-level Mean and No Covariate}
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.3]{school1.png}
\caption{Shrinkage and interval plots of 8 schools}
\end{center}
\end{figure}
